---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


```{r}
library(tidyverse)
```

```{r}
paintings <- read_csv("paris-paintings (1).csv")
```

What are the columns?
```{r}
names(paintings)
```
What is the effect of painting width on price? Is it positive or negative?
```{r}
width_price <- lm(Width_in ~ price, data = paintings )

summary(width_price)

print("The effect is positive and significant.")
```

```{r}
sunburns <- read_csv("sunburns.csv")
names(sunburns)
```
What is the effect of ice cream sales on sunburns? Is it positive or negative? Is it significant? What is
weird about this finding? What could be going on?

```{r}
icecream_sunburns <- lm(sunburns ~ icecreams, data = sunburns)
summary(icecream_sunburns)

print("The effect is estimated to be 0.0004230. positive and significant. It is weird that the number is small but significant. Different scales of both observations.")
```
Now what is the effect of temperature on sunburns? Is it positive or negative? Is it significant?
```{r}
temp_sunburns <- lm(sunburns ~ temperature, data = sunburns)
summary(temp_sunburns)

print("The effect is positive and significant at 0.22312.")
```

Next, what is the effect of temperature on ice cream sales? Positive / negative? Is it significant?
```{r}
temp_icecream <- lm(icecreams ~ temperature, data = sunburns)
summary(temp_icecream)

print("There is a significant and large effect of temperature on ice cream sales at 338.55.")
```
Finally, what is the effect of ice cream sales on sunburns after controlling for temperature? How do
you interpret this finding?
```{r}
icecream_sunburns_controlled <- lm(sunburns ~ icecreams + temperature, data = sunburns)
summary(icecream_sunburns_controlled)

print("The effect is not significant after controlling. It means that ice cream sales have no significant effect on sunburns, and it's only temperature that has a significant effect.")
```
What story do these four regression models uncover? Does a significant effect size always mean there
is a true effect of a variable on another variable?
```{r}
print("Control first then see significance!!! Significant effect does not necessarily mean true effect, where multiple variables are involved due to confounders. ")
```

