---
title: "R Notebook"
output:
  pdf_document: default
---

## Loading of Data

```{r, message = FALSE}
library(tidyverse)
beauty <- read_csv("beauty.csv")
```

Filtering to only female respondents:

```{r}
beauty_data <- beauty %>% filter(gender == "Female")
```

Demographic characteristics:

```{r}
fivenum(beauty_data$age)
unique(beauty_data$faculty)
fivenum(beauty_data$tiktok_hours)
beauty_data %>% mutate(beauty_index = tiktok_hours*frequency) -> beauty_data
```

## T-tests between IV and DVs

First, split respondents into two groups: those who do not consume beauty content on Tiktok (ie. Watched Hours = 0 + Tiktoks related to beauty answer "not at all"), and those who do.

```{r}
beauty_false <- beauty_data %>% filter(tiktok_hours == 0 | frequency == 1)
beauty_true <- setdiff(beauty_data, beauty_false)

```

Then, compare means of dependent variables.

For self-esteem, our hypothesis is that the self-esteems of those who consume beauty content are lower than those who do not. t = 1.2579, p = 0.8907. Hence, the longer-term self-esteems of those who consume beauty content is not significantly lesser than those who do not.

```{r}
t.test(beauty_true$high_self_esteem, beauty_false$high_self_esteem, alternative = "less")
```

For appearance anxiety, our hypothesis is that those who consume beauty content experience more appearance anxiety than those who do not. t = 1.0299, , p-value = 0.156. Hence, the longer-term appearance anxiety of those who consume beauty content is not significantly greater than those who do not.

```{r}
t.test(beauty_true$anxiety, beauty_false$anxiety, alternative = "greater")
```

For mood, our hypothesis is that those who consume beauty content have their moods more negatively affected by such content than those who do not. t = 2.9167, p-value = 0.003428. Hence, the moods of those who consume beauty content are significantly more negatively affected than those who do not.

```{r}
t.test(beauty_true$negative_mood, beauty_false$negative_mood, alternative = "greater")
```

## Simple Linear Regression between IV and DVs

```{r}
beauty_mood <- lm(negative_mood ~ beauty_index, data = beauty_data)
summary(beauty_mood)
```


```{r}
beauty_anxiety <- lm(anxiety ~ beauty_index, data = beauty_data)
summary(beauty_anxiety)
```


```{r}
beauty_esteem <- lm(high_self_esteem ~ beauty_index, data = beauty_data)
summary(beauty_esteem)
```

```{r}
beauty_jealousy <- lm(jealousy ~ beauty_index, data = beauty_data)
summary(beauty_jealousy)

beauty_comparison <- lm(comparison ~ beauty_index, data = beauty_data)
summary(beauty_comparison)
```

```{r}
beauty_self_esteem_after <- lm(self_esteem_awareness ~ beauty_index, data = beauty_data)
summary(beauty_self_esteem_after)

beauty_anxiety_after <- lm(anxiety_after ~ beauty_index, data = beauty_data)
summary(beauty_anxiety_after)
```

## Confounders

We have identified consumption of beauty content from other platforms outside of Tiktok as a possible confounder for the correlations between our IV and DVs. Our confounder hence becomes the variable of the number of other platforms used outside of Tiktok, found through mutating a new column from the data in beauty_data\$platforms.

```{r tidy=TRUE, tidy.opts=list(width.cutoff=60)}
mutate(beauty_data, other_platforms = str_remove_all(beauty_data$platforms, "Tiktok/ Douyin;")) -> beauty_data
mutate(beauty_data, other_platforms = str_remove_all(beauty_data$other_platforms, "Tiktok/ Douyin")) -> beauty_data
beauty_data$other_platforms[beauty_data$other_platforms == ""] <- NA
beauty_data$other_platforms <- trimws(beauty_data$other_platforms, "r", whitespace = ";")
mutate(beauty_data, n_other_platforms = str_count(beauty_data$other_platforms, ";") + 1) -> beauty_data

```


```{r}
beauty_anxiety_conf <- lm(anxiety ~ beauty_index + n_other_platforms, data = beauty_data)
summary(beauty_anxiety_conf)
```

```{r}
beauty_esteem_conf <- lm(high_self_esteem ~ beauty_index + n_other_platforms, data = beauty_data)
summary(beauty_esteem_conf)
```
```{r tidy=TRUE, tidy.opts=list(width.cutoff=60)}
#Identifying if there is R/S between n_other_platforms and beauty_index since confounders usually entail R/S between confounder, IV, DV.
beauty_index_platforms <- lm(n_other_platforms ~ beauty_index, data = beauty_data)
summary(beauty_index_platforms)

beauty_index_platforms2 <- lm(beauty_index ~ n_other_platforms, data = beauty_data)
summary(beauty_index_platforms2)
```


We do not repeat the test for confounders on the single linear regression model between beauty Tiktok consumption and mood because the question for that set of observations surveys for a cause and effect relationship between Tiktok consumption specifically and mood ("negative changes in your mood (e.g., increased sadness or self consciousness) *after* watching beauty TikTok video") for non-neutral answers.


## Antecedent vs Post-Tiktok levels of anxiety and self-esteem
```{r}
beauty_index_anxiety_controlled <- lm(anxiety_after ~ beauty_index + anxiety, data = beauty_data)
summary(beauty_index_anxiety_controlled)

anxiety_anxiety_after <- lm(anxiety_after ~ anxiety, data = beauty_data)
summary(anxiety_anxiety_after)

beauty_index_selfesteem_controlled <- lm(self_esteem_awareness ~ beauty_index + high_self_esteem, data = beauty_data)
summary(beauty_index_selfesteem_controlled)

beauty_index_inadequacy_controlled <- lm(jealousy ~ beauty_index + high_self_esteem, data = beauty_data)
summary(beauty_index_inadequacy_controlled)

```

## Construct validity/Agreement between questions 

Mood: hypothesis: correlation between beauty index and positive mood from tiktok should be inverse of correlation between beauty index and negative mood from tiktok 
```{r}
beauty_positive_mood <- lm(positive_mood ~ beauty_index, data = beauty_data)
summary(beauty_positive_mood)

beauty_mood <- lm(negative_mood ~ beauty_index, data = beauty_data)
summary(beauty_mood)
```

Self-esteem: hypothesis: correlation between beauty index effect on detrimental mood after tiktok and correlation between beauty index effect on pressured to change oneself/
```{r}
beauty_positive_mood <- lm(positive_mood ~ beauty_index, data = beauty_data)
summary(beauty_positive_mood)
```


```{r}
beauty_unrealistic <- lm(unrealistic ~ beauty_index, data = beauty_data)
summary(beauty_unrealistic)

beauty_unhealthy <- lm(unhealthy ~ beauty_index, data = beauty_data)
summary(beauty_unhealthy)

beauty_pressure <- lm(pressure ~ beauty_index, data = beauty_data)
summary(beauty_pressure)

unrealistic_unhealthy_anxiety_after <- lm(anxiety_after ~ unrealistic + unhealthy, data = beauty_data)
summary(unrealistic_unhealthy_anxiety_after)
```

